---
title: "Text Mining Workshop"
description: |
  An introduction to analyzing text data
site: distill::distill_website
output:
  distill::distill_article:
    toc: true
author:
  - first_name: "Julia"
    last_name: "Silge"
    url: https://juliasilge.com/
    affiliation: RStudio PBC
    affiliation_url: https://www.rstudio.com
    orcid_id: 0000-0002-3671-836X
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```


## Welcome

These are the materials for workshops on text analysis by [Julia Silge](https://juliasilge.com/). Text data is increasingly important in many domains, and tidy data principles and tidy tools can make text mining easier and more effective. In this workshop, learn how to manipulate, summarize, and visualize the characteristics of text using these methods and R packages from the tidy tool ecosystem. These tools are highly effective for many analytical questions and allow analysts to integrate natural language processing into effective workflows already in wide use. Explore how to implement approaches such as sentiment analysis of texts, measuring tf-idf, network analysis of words, and building both supervised and unsupervised text models.

## Is this workshop for me?

This course will be appropriate for you if you answer yes to these questions:

- Have you ever encountered text data and suspected there was useful insight latent within it but felt frustrated about how to find that insight?
- Are you familiar with dplyr and ggplot2, and ready to learn how unstructured text data can be analyzed within the [tidyverse](https://www.tidyverse.org/) ecosystem?
- Do you need a flexible framework for handling text data that allows you to engage in tasks from exploratory data analysis to supervised predictive modeling?


## Learning objectives

At the end of this workshop, participants will understand how to: 

- Perform exploratory data analyses of text datasets, including summarization and data visualization
- Understand and implement both sentiment analysis and tf-idf
- Use unsupervised models to gain insight into text data
- Build supervised classification models for text using tidy data principles


## Preparation

Please tune into the workshop with a computer that has the following installed (all available for free):

- A recent version of R, available at https://cran.r-project.org/
- A recent version of RStudio Desktop (RStudio Desktop Open Source License), available at https://www.rstudio.com/download
- The following R packages, which you can install by connecting to the internet, opening RStudio, and running at the command line:

```{r eval=FALSE, echo=TRUE}
install.packages(c("tidyverse", "tidytext", 
                   "gutenbergr",
                   "stopwords", "stm",
                   "tidymodels", "glmnet", 
                   "vip", "textrecipes"))

```

## Slides

- 00: [Intro](slides/00-intro.html)
- 01: [Text as tidy data](slides/01-tidytext.html)
- 02: [More advanced EDA](slides/02-more-eda.html)
- 03: Topic modeling
- 04: Supervised text models

## Past workshops

- [16 October 2017 for Portland R-Ladies and Portland R User Group](https://www.meetup.com/R-Ladies-PDX/events/243376514/)
- [18 April 2018 for R-Ladies RTP](https://www.meetup.com/R-Ladies-RTP/events/248456720/)
- [22 May 2018 for III International Seminar on Statistics with R](https://ser2018.weebly.com/programmee.html)
- [29 May 2019 for ASA Symposium on Data Science and Statistics](https://github.com/juliasilge/sdss2019)
- [27-28 January 2020 at rstudio::conf()](https://education.rstudio.com/blog/2020/02/conf20-tidytext/)
- [10 February 2021 for National Institute of Statistical Sciences](https://www.niss.org/events/essential-data-science-business-unstructured-data-analysis-text-mining-tidy-data-principles)



## Acknowledgments {.appendix}

This website is made with [distill](https://rstudio.github.io/distill/) and the slides are made with [xaringan](https://github.com/yihui/xaringan), both based on [R Markdown](https://rmarkdown.rstudio.com/).

## Corrections {.appendix}

Please [submit an issue](https://github.com/juliasilge/tidytext-tutorial/issues) on the GitHub repo for this workshop if you find something that could be fixed or improved.

## Reuse and licensing {.appendix}

Unless otherwise noted (i.e. not an original creation and reused from another source), these educational materials are licensed under Creative Commons Attribution [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/).
