---
title: "Text mining with tidy data principles: text classification"
author: "Julia Silge"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
my_mirror <- "http://mirrors.xmission.com/gutenberg/"
```

## Download data

First download data to use in modeling:

https://www.gutenberg.org/browse/scores/top

Choose two books you want to use in modeling.

```{r}
library(tidyverse)
library(gutenbergr)

titles <- c("The War of the Worlds",
            "Pride and Prejudice")

books <- gutenberg_works(title %in% titles) %>%
    gutenberg_download(meta_fields = "title", mirror = my_mirror) %>%
    mutate(title = str_replace_all(title, " ", "_")) %>%
    filter(nchar(text) > 3) %>%
    mutate(document = row_number())

books
```

## Spend your data budget

We can start out by splitting our data into training and testing sets.

```{r}
library(tidymodels)

set.seed(123)
book_split <- initial_split(books, strata = title)
book_train <- ___
nrow(book_train)

book_test <- ___
nrow(book_test)
```

We should _not_ use the test set for choosing, comparing, or tuning models, so we can create resampled data sets as well.

```{r}
set.seed(234)
book_folds <- vfold_cv(book_train, strata = title)
book_folds
```

## Specify a model

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
lasso_spec <- logistic_reg(___) %>%
    set_engine("glmnet")

lasso_spec
```

## Feature engineering

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
book_rec <- recipe(title ~ text, data = book_train) %>%
    ___  %>% 
    ___ %>%  
    step_tokenfilter(text, max_tokens = 500) %>%
    step_tfidf(text)

book_rec
```


## Tune a model `workflow()`

```{r}
book_wf <- workflow() %>%
    add_recipe(book_rec) %>%
    add_model(lasso_spec)

book_wf
```

```{r}
narrower_penalty <- penalty(range = c(-5, 0))

set.seed(2021)
lasso_grid <- tune_grid(
    ___,
    resamples = book_folds,
    param_info = parameters(narrower_penalty),
    grid = 20
)

lasso_grid
```

## Choose and evaluate final model

Which model was the best? We can choose the simplest model that is within one standard error of the optimal result.

```{r}
show_best(lasso_grid)

autoplot(lasso_grid)

simple_lasso <- select_by_one_std_err(
    lasso_grid, 
    ___, 
    metric = "roc_auc"
)

simple_lasso
```

Now let's finalize our original, tunable workflow with this set of parameters and then **fit** to the training data and **evaluate** on the testing data. This is the first time we have touched the testing data.

```{r}
book_final <- book_wf %>%
    finalize_workflow(simple_lasso) %>%
    ___(book_split)

collect_metrics(book_final)
```

How did the model perform on the testing data?

```{r}
collect_predictions(book_final)

collect_predictions(book_final) %>%
    ___(title, .pred_class)

collect_predictions(book_final) %>%
    ___(title, .pred_Pride_and_Prejudice) %>%
    autoplot()
```

## Variable importance

Which variables (words) were most importance in driving a prediction more toward one title vs. the other? This computation uses the fitted workflow/model we just trained.

```{r}
library(vip)

book_vip <- book_final$.workflow[[1]] %>%
    pull_workflow_fit() %>%
    vi()

book_vip
```

```{r}
book_vip %>%
    group_by(Sign) %>%
    ___(abs(Importance), n = 15) %>%
    ungroup() %>%
    mutate(
        Importance = abs(Importance),
        Variable = fct_reorder(Variable, Importance)
    ) %>%
    ___ +
    geom_col() +
    facet_wrap(~Sign)
```


**GO EXPLORE REAL-WORLD TEXT!**

Thanks for learning with me! <3
